---
title: "July Effect - Preliminary"
author: "Mustafa Ascha"
date: "January 29, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, error = FALSE, message = FALSE)
library(pander)
library(tidyverse)
library(mice)

devtools::document()
#devtools::build()
devtools::load_all()

otl <- outcomes_list <- list()
otl[["everyone"]] <- paste0(c("returnor", "supinfec"), "_01")
otl[["cosmetics"]] <- paste0(c("returnor", "supinfec"), "_01")
otl[["no_cosmetic"]] <- paste0(c("returnor", "supinfec"), "_01")

```


```{r read data}
nsqip <- 
  map(c("everyone", "cosmetics", "no cosmetics"), 
      function(which_df) make_nsqip(1:6, which_df)) 
names(nsqip) <- c("everyone", "cosmetics", "no_cosmetic")
```

```{r make table ones}
#tbl_ones_pgy <- map(nsqip, tbl_one, strat = "pgy_bin")

nsqip <- map(nsqip, function(df) mutate(df, admqtr_t = ifelse(admqtr == "0", "Any Quarter", admqtr)))
tbl_ones <- 
  map(nsqip, 
      function(df, strat) {
        print(tableone::CreateTableOne(c("surgspec", "pgy_bin", 
                                         paper_stuff$mona$predictors, 
                                         paper_stuff$vti$outcomes), 
                             strata = "admqtr_t", data = df), printToggle = FALSE)
  })

```

```{r setup propensity score dataframe, results = 'hide'}

nsqip <- nsqip %>% map(function(df){
  preds <- nsqipr::paper_stuff$mona$predictors
  the_form <- paste0("pgy01 ~ ", paste0(preds, collapse = " + "))
  df[["propensity_score"]] <-
    predict(glm(the_form, "binomial", df), df, type = "response")
  df
})

paper_stuff$mona[["predictors"]] <-
   c(nsqipr::paper_stuff$mona[["predictors"]], "propensity_score")

nsqip <- nsqip %>% map(binarize_outcomes)
#check which variables are cool
#map(nsqip, function(x) map(x[paper_stuff$mona$outcomes], table))

nsqip <- 
  map(nsqip, function(df){
    list(select(df, "pgy01", "pgy_bin", "admqtr", "admqtr23_01",
                one_of(nsqipr::paper_stuff$mona$predictors, 
                       unique(unlist(otl)))), 
         select(df,  "propensity_score"))
    })
pscores <- map(nsqip, 2)
nsqip <- 
  map(nsqip, 1) %>% 
  map(function(df) select(df, -admqtr23_01))

not_imputed_nsqip <- nsqip

impute_fn <- function(df) mice(df, m=1, maxit=50, seed=400, ridge=0.01)
nsqip <- map(nsqip, function(df) mice::complete(impute_fn(df), 1))
nsqip <- map2(nsqip, pscores, function(x, y) na.omit(bind_cols(x, y)))

matched_data <- 
  map(nsqip, function(df) {
  MatchIt::match.data(MatchIt::matchit(pgy01 ~ 
                       age + sex + bmi + race + smoke + 
                       diabetes + hypermed + workrvu + 
                       optime + inout + tothlos + wndclas + 
                       asaclas + attend, 
                     method = "nearest", data = df))
  })

unmatched_data <- nsqip

#match_fn(nsqip[[1]])
```

# Missingness

```{r}
proportion_missing <- 
  map_df(not_imputed_nsqip, 
      function(df) map_dbl(df, ~ length(which(is.na(.x))) / length(.x))) %>% 
  mutate(average = (everyone + cosmetics + no_cosmetic) / 3, 
         Variable = names(not_imputed_nsqip[[1]]))
pander(proportion_missing, caption = "Proportion of missing observations for each variable. These were imputed.")
```



```{r model and tidy models, results = 'hide'}

glms <- do_glms(matched_data, unmatched_data)

aucs <- 
  map2(glms, names(glms), classification_metrics) %>% 
  flatten_dfr() %>% 
  modify_at(c("c_stat", "h_l_stat"), ~ sprintf("%.3f", .x))

aucs$outcome <- gsub("_01$", "", aucs$outcome)


tidied_models <-
  map2(glms, names(glms),
       function(dflist, dfnm) {
         map(dflist, function(mdl) {
           mutate(broom::tidy(mdl[[1]]), glm = dfnm, outcome = mdl[[2]])
             })
         }) %>% 
  flatten_dfr


confint_models <-
  map2(glms, names(glms),
       function(dflist, dfnm) {
         map(dflist, function(mdl) {
           cbind(confint(mdl[[1]]), glm = dfnm, outcome = mdl[[2]])
           })
         }) %>% 
  (function(matrices_list){
    matrices_list <- flatten(matrices_list)
    the_rownames <- unlist(map(matrices_list, rownames))
    the_df <- bind_rows(map(matrices_list, data.frame, stringsAsFactors = FALSE))
    the_df[["rownames"]] <- the_rownames
    names(the_df) <- c("conf.lower", "conf.upper", "glm", "outcome", "term")
    the_df
  })



models_df <- full_join(tidied_models, confint_models)
models_df <-
  models_df[,!grepl("1$", names(models_df))] %>%
  select(-statistic, -std.error)

to_exp <- c("estimate", "conf.lower", "conf.upper")
models_df[,to_exp] <- lapply(models_df[,to_exp], function(x) {
  sprintf("%.4f", exp(as.numeric(x)))})

for_show <- c("term", "glm", "outcome", "estimate", "conf.lower", "conf.upper", "p.value")
models_df <- models_df[,for_show]
models_df$outcome <- gsub("_01$", "", models_df$outcome)

models_df <- models_df %>% 
  filter(!(term %in% c("(Intercept)", "propensity_score"))) 

models_df$propensity <- 
  ifelse(grepl("no_prop", models_df$glm), "Unmatched", "Matched")

models_df$population <- gsub("no_prop_", "", models_df$glm)
models_df$population <- gsub("_", " ", models_df$population)

to_replace <- 
  c("admqtr2", "admqtr3", 
    "pgy_binFour or above", "pgy_binThree\\ or\\ lower")
replacements <- c("Q2", "Q3", "PGY4+", "PGY3-")

models_df$term <- 
  reduce2(to_replace, replacements, 
          function(innit, tr, rep) gsub(tr, rep, innit), 
          .init = models_df$term)

fxr_uppers <- 
  with(models_df, as.numeric(estimate) == 0 |
                 as.numeric(conf.upper) > 10 |   
                 is.na(conf.lower))
fxr_uppers <- ifelse(is.na(fxr_uppers), TRUE, fxr_uppers)

models_df[fxr_uppers,c("estimate", "conf.lower", "conf.upper", "p.value")] <- 
  NA

to_show <- 
  c("term", "population", "propensity", "outcome", 
    "estimate", "conf.lower", "conf.upper", "p.value", 
    #"c_stat", 
    "h_l_stat")

models_df <- left_join(models_df, aucs)

models_df <- models_df[,to_show]

```

# Table ones

## Whole Population

```{r}
pander(tbl_ones[[1]][,1:3])
```


## Cosmetics procedures

```{r}
pander(tbl_ones[[2]][,1:3])
```


## Non-cosmetics procedures

```{r}
pander(tbl_ones[[3]][,1:3])
```

\pagebreak 

# Odds of outcome during 3rd quarter

Here, we are looking at an estimate of the odds ratio of an outcome for the third quarter compared to the second quarter, PGY3 and below versus PGY4 and above. Each estimate in the following two tables that corresponds to the same outcome, population, and "propensity" label is the result of a single logistic regression model, where these models are predicted by each of admission quarter (3 versus any other), resident involvement, and propensity score + matching for the "Matched" populations.  


```{r}
pander(models_df %>% filter(term == "Q3") %>% arrange(desc(outcome, propensity)), split.table = Inf)
```

```{r}
pander(models_df %>% filter(term != "Q3") %>% arrange(desc(outcome, propensity)), split.table = Inf)
```


# Propensity score visualization 

These visualizations are meant to ensure comparable propensity scores. If one of the populations has a visually different number of observations in a particular propensity score range, then we would be concerned that propensity scoring didn't work. 

```{r}

propplot <- function(df) ggplot(df, aes(propensity_score, fill = admqtr)) + geom_histogram()

map(nsqip, propplot)

```



```{r}

devtools::session_info()

```







